### 2022-06-16 doc/VerticalArrangements.tex
removed nests summary from summary table. started fixing text in paper.

The median average wholesale pre-merger price is \$5.20, and the median average retail pre-merger price is \$14.  Recall that the market size is set to 1, meaning that average price is equal to total pre-merger expenditures.  Pre-merger HHIs range from 2,923 at the $25^{th}$ percentile to 4,966 at the $75^{th}$, with a median of 3,742. HHIs for vertical mergers increase by 1,328 points at the median, resulting in a median post-merger HHI equal to 6,046.\footnote{We compute the post-merger HHI for vertical mergers by treating the merged firms' market share as the sum of all the shares of downstream products that either use the upstream partner's input or are sold by the downstream partner.  }  HHIs for downstream mergers increase by 2,044 points at the median, resulting in a median post-merger HHI equal to 4,916.  HHIs for upstream mergers increase by 2,023 points at the median, resulting in a median post-merger HHI equal to 4,916. HHIs for integrated mergers increase by 2,822 points at the median, resulting in a median post-merger HHI equal to 7,135.

@@

We focus first on the results for consumers in the left-most panel of Figure \ref{fig:surplussum}.  Less than half of all simulated vertical mergers are harmful, while the majority of upstream, downstream, and integrated mergers show harm.  In particular, there is a partial rank-ordering of consumer harm across types of mergers: consumer harm from integrated mergers first-order stochastically dominates consumer harm from all other merger types, while downstream and upstream mergers each first-order stochastically dominate consumer harm from vertical mergers, but do not stochastically dominate one other.   Median consumer harm from integrated mergers is 14\% of pre-merger total expenditures, 1.45 times the magnitude of that from downstream mergers, and 3.1 times the magnitude of that from upstream mergers.

>>>>

The median average wholesale pre-merger price is \$5.80, and the median average retail pre-merger price is \$15.  Recall that the market size is set to 1, meaning that average price is equal to total pre-merger expenditures.  Pre-merger HHIs range from 2,911 at the $25^{th}$ percentile to 4,980 at the $75^{th}$, with a median of 3,747. HHIs for vertical mergers increase by 1,328 points at the median, resulting in a median post-merger HHI equal to 6,045.\footnote{We compute the post-merger HHI for vertical mergers by treating the merged firms' market share as the sum of all the shares of downstream products that either use the upstream partner's input or are sold by the downstream partner.  }  HHIs for downstream mergers increase by 2,126 points at the median, resulting in a median post-merger HHI equal to 5,149.  HHIs for upstream mergers increase by 2,069 points at the median, resulting in a median post-merger HHI equal to 4,967. HHIs for integrated mergers increase by 2,801 points at the median, resulting in a median post-merger HHI equal to 7,135.

@@

We focus first on the results for consumers in the left-most panel of Figure \ref{fig:surplussum}.  Less than half of all simulated vertical mergers are harmful, while the majority of upstream, downstream, and integrated mergers show harm.  In particular, there is a partial rank-ordering of consumer harm across types of mergers: consumer harm from downstream and integretaed mergers first-order stochastically dominates consumer harm from upstream mergers which in turn dominates consumer harm from vertical mergers. However, while consumer harm is typically greater under integrated mergers than downstream mergers, it is not first-order stochastically dominant. Median consumer harm from integrated mergers is about 14\% of pre-merger total expenditures, 1.3 times the magnitude of that from downstream mergers, and 3 times the magnitude of that from upstream mergers.
